An efficient acyclic contact planner for multiped robots

### 2016-01-19 body/appendix_roms.tex
complete, need abstract and section 4

\subsection{Step 2: computing the trunk scaling workspace $W^0$ of the robot}
To define the volume $W^0$ of HRP-2, we proceed in an empirical manner.
First, we compute the bounding boxes of the robot trunk, head, and upper legs (Figure~\ref{fig:hrp2_w} -- red shapes).
Then, we perform a scaling of these boxes by a factor $s$. For different values of $s$, we verify the geometrical feasibility condition:
For a large number of configurations that verify the \gls{reachc}, we try to generate contact configurations. We then
empirically select the lowest value of $s$ that provides a reasonnable success rate in all scenarios.
For HRP-2, we choose $s=1.2$. This leads to a success rate higher than 86 \% for all scenarios.

>>>>

\subsection{Step 2: computing the trunk scaling workspace $W^0$ of the robot}
To define the volume $W^0$ of HRP-2, we proceed in an empirical manner.
First, we compute the bounding boxes of the robot trunk, head, and upper legs (Figure~\ref{fig:hrp2_w} -- red shapes).
Then, we perform a scaling of these boxes by a factor $s$. 
The higher $s$ is, the more likely sampled configurations are to be feasible, but the less complete is the approach.
To compute the appropriate value of $s$, we proceed as described in Section~\ref{sec:params}, and choose empirically
$s^*=1.2$ as the appropriate value for HRP-2.

### 2016-01-19 body/glossary.tex
complete, need abstract and section 4

\newglossaryentry{cluttered}
{
  name=cluttered,
  description={A class of contact planning problems that admit as a solution a sequence of contact configurations for which at least one contact occurs with a \gls{quasi-flat} surface}
}

@@

\newglossaryentry{interactive}
{
  name=interactive,
  description={We say that a planning method is \gls{interactive} when the computation time for one step is lesser than the
time to execute it. We arbitrarily approximate this time to one second.}
}

>>>>

\newglossaryentry{cluttered}
{
  name=\textit{cluttered},
  description={A class of contact planning problems that admit as a solution a sequence of contact configurations for which at least one contact occurs with a \gls{quasi-flat} surface}
}

@@

\newglossaryentry{interactive}
{
  name=\textit{interactive},
  description={We say that a planning method is interactive when the computation time for one step is lesser than the
time to execute it. We arbitrarily approximate this time to one second}
}

### 2016-01-19 body/results.tex
complete, need abstract and section 4

@@

\begin{table*}
\centering
\begin{tabular}{ l | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | c}
  &  Path planning & Equilibrium feasibility & Kinematic failure & Equilibrium failure \\
 \hline
   Steep stairs & 100\%  & 99.5\% & 0.11\% & 0.39\% \\
   Standing up & 68\% & 88\% & 6\% & 6\% \\
   Car egress & 39\% & 77\% & 21\% &  2\% \\
   Rubble & 74\% & 97.87\% & 0.13\% & 2\% \\
   Obstacle race & 58\% & 95.7\% & 1.8\% & 2.5\% \\
 \end{tabular}
\caption{Success rates for each scenario. The first value indicates the percentage of successful complete contact plannings for 1000 tests; The second value
indicates the percentage of equilibrium feasible root configurations: considering each limb individually, indicates the percentage of root configurations of the guide path that
led to a feasible contact. Kinematic failure is the percentage of contact generations that failed because no collision-free candidate was found. Equilibrium failure is the percentage of contact
generations that failed because no candidate respected the static equilibrium condition.}
\label{tab:requestpercent}
\quad
\end{table*}

@@

>>>>

\subsection{Influence of the parameters} \label{sec:influence}
We discuss the several factors can influence the outcome of our planner: the root scaling factor $s$, the choice of heuristics for
contact generation, the parametrization of the static equilibrium robustness, and lastly, the discretization 
of the guide path.

\subsubsection{Choosing the scaling factor $s$} \label{sec:params}
To find a convenient value $s^*$ of $s$, we proceeded as follows. 
For several values of $s$, we generated $10 000$ configurations. 
We then computed the rates of false positives (ie the resulting configuration satisfies
the reachability condition, but does not belong to \gls{ccontact0}) and false negatives (ie the resulting configuration does not satisfy the 
reachability condition, but belongs to \gls{ccequil0}).

The obtained results for HRP-2 are summarized in Table~\ref{tab:scale}, averaged over all scenes (except for the car egress: in this scenario, 
statistical tests are not really conclusive since we are only interested in a small area of the environment).
As it can be expected, the scaling results in a high increase of the false negative, while the false positive decreases.
For HRP-2 we decided to set $s^*=1.2$, that results in less than 3 \% of false positives, and was also effective
for the car egress scenario.

\begin{table}
\centering
\footnotesize
\begin{tabular}{c | c | c}
   Value of $s$ &  False positive & False negative\\
 \hline
   1   & 24\% & 0 \%\\
   1.1& 12\% & 4\% \\
   1.15& 07\% & 6\%\\
   1.2 & 03\% & 7.5\%\\
   1.25& 02\% & 8.3\%\\
   1.5 & 01\% & 9.5\%\\
 \end{tabular}
\caption{Percentage of true and false positive in the reachability condition, depending on the scaling value of $W^0$.}
\label{tab:scale}
\quad
\end{table}

\subsubsection{On the choice of heuristics} \label{sec:heuristics}
In our conference paper, the computed motions were only generated using the EFORT heuristic.
EFORT is designed for tasks requiring to exert important forces (such as pushing / pulling / climbing). 
Regarding locomotion tasks, such as the stair scenario, one issue with EFORT is that it tends to generate
configurations close to singularities (and joint limits). While this does not significantly impact
the generation of the plan, the resulting interpolation on the real robot turned out to be harder \citep{Carpentier2016}.
For this reason, we now prefer to use our manipulability based heuristic for the legs of the robot, but we still
use EFORT for the arm, that results in lesser contact repositionning.

\subsubsection{parametrization of the robustness equilibrium criterion} \label{sec:parrob}
Robustness is really important when considering practical applications on the robot, to account 
for the various uncertainties that result from environment and state estimator. However,
maximizing the robustness criterion is not necessarily optimal, because the resulting contacts will stay close to the center
of mass, thus not favoring the motion. In our experiments, we choose not to maximize the robustness,
but to empirically set a robustness treshold value under which a configuration is not considered to be in
static equilibrium (If no candidate reaches the treshold, instead of failing, the algorithm can eventually return the ``more robust'' configuration
found). Currently for HRP-2, a treshold value of 2 subjectively gives the best results in the considered scenarios, while 10 seems to be a good choice for HyQ. Both values do not
significantly slow down the planning times.

\subsubsection{Discretization of the guide path} \label{sec:disc}
Currently, to discretize the path, the user defines a fixed step size. The step size
has an influence on the output of the planner: if too large steps are taken,
the planner may fail since we impose the constraint that only one contact change might occur
between two consecutive stances. For instance, in most scenarios the torso of HRP-2 translates by about 15 cm between two postures, but about only 3 cm
for the car egress scenario for instance, where we had to lower the step size because of the many contact breaks, induced by the extremely constrained geometry.
For future work, we would like to automatically adapt the size of the discretization step to the complexity of the planning, for instance
by reducing the step size when in the areas where failure occur.

@@

\begin{table*}
\centering
\begin{tabular}{ l | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | >{\centering\arraybackslash}m{65pt} | c}
  &  Path planning & Equilibrium feasibility & Kinematic failure & Equilibrium failure \\
 \hline
   Steep stairs & 100\%  & 99.5\% & 0.1\% & 0.4\% \\
   Standing up & 68\% & 87.8\% & 6.1\% & 6.1\% \\
   Car egress & 39\% & 77.0\% & 21.0\% &  2.0\% \\
   Rubble & 74\% & 97.9\% & 0.1\% & 2.0\% \\
   Obstacle race & 58.0\% & 95.7\% & 1.8\% & 2.5\% \\
 \end{tabular}
\caption{Success rates for each scenario, rounded to the first decimal. The first value indicates the percentage of successful complete contact plannings for 1000 tests; The second value
indicates the percentage of equilibrium feasible root configurations: considering each limb individually, indicates the percentage of root configurations of the guide path that
led to a feasible contact. Kinematic failure is the percentage of contact generations that failed because no collision-free candidate was found. Equilibrium failure is the percentage of contact
generations that failed because no candidate respected the static equilibrium condition.}
\label{tab:requestpercent}
\quad
\end{table*}

@@

\begin{table*}
\centering
\begin{tabular}{ c | c | c | c | c }
 Scenario & Method  & Guide Path & Contact sequence & Interpolation \\
 \hline
   \multirow{3}{*}{Stair 20 cm} & \citeauthor{Hauser06usingmotion} &  \multicolumn{3}{c}{5.42 min}  \\
							 & \citeauthor{Mordatch:2012:DCB:2185520.2185539} &  \multicolumn{3}{c}{2 to 10 min} \\
							 & \textbf{Ours} + \citeauthor{Carpentier2016}  & $\mathbf{<}$ \textbf{2 ms} & $\mathbf{<}$ \textbf{14 ms} & $ <$ 2s \\
 \hline
   \multirow{3}{*}{Stair 30 cm} & \citeauthor{Hauser06usingmotion} &  \multicolumn{3}{c}{4.08 min}  \\
							 & \citeauthor{Mordatch:2012:DCB:2185520.2185539} &  \multicolumn{3}{c}{2 to 10 min} \\
							 & \textbf{Ours}  & $\mathbf{<}$ \textbf{2 ms} & $\mathbf{<}$ \textbf{14 ms} & X \\
 \hline
   \multirow{3}{*}{Stair 40 cm} & \citeauthor{Hauser06usingmotion} &  \multicolumn{3}{c}{10.08 min}  \\
							 & \citeauthor{Mordatch:2012:DCB:2185520.2185539} &  \multicolumn{3}{c}{2 to 10 min} \\
							 & \textbf{Ours}  & \textbf{5 s} & \textbf{3 s} & X \\
 \hline
   \multirow{2}{*}{Table (car) egress} & \citeauthor{Bouyarmane2009, DBLP:conf/iser/EscandeKMG08} & 10 min & \multicolumn{2}{c}{3.5 hours}  \\
							 & \textbf{Ours}  & \textbf{529 ms} & \textbf{$<$ 21 s} & X \\
 \end{tabular}
\caption{TODO VERIFIE STATS A LA MAISON.}
\label{tab:compprev}
\quad
\end{table*}
\subsection{Comparison with previous work} \label{sec:compa}
Comparing our method with others is not trivial. Indeed, we focus on the contact planning aspect of the problem, and do not address
the interpolation in this paper, nor provide a strong guaranty that our sequence can be interpolated.
Papers in the state of the art, when they indicate the computation times, often only provide an overall computation
time, and we can not afford the important development resources required to reimplement them.

Furthermore, the interpolation itself is a problem that is far from being solved. For instance in \cite{DBLP:conf/iser/EscandeKMG08}, the end-effector trajectories are computed automatically with splines, but are manually corrected if they enter in collision. In \citep{Mordatch:2012:DCB:2185520.2185539}, internal joint collisions can occur in the resulting motion.
Recent methods suffer from similar issues \citep{Carpentier2016}.

Regardless, we indicate in Table~\ref{tab:compprev} what is actually computed by the method and in how much time.
We compare motions obtained in previous works with HRP-2 (or a humanoid avatar) with ours: the two scenarios we selected consist in:  climbing one step, high of 20, 30 or 40 centimeters; 
moving out of a table, that we consider of a complexity similar to the car egress scenario (or inferior since the feet location remain on the ground in the former case).
For scenarios that apply, we also indicate the interpolation time that we obtain by feeding the plan to our interpolation method presented in \cite{Carpentier2016}.

Despite the difficulty of comparing the methods, we believe the results presented in Table~\ref{tab:compprev} indicate that our planner holds the promise of planning complete trajectories significantly faster than previous works.
